### 2012-10-01 MSteenhagen-CV.tex
New CV created. Needs polishing.

%%% A template to produce a nice-looking Curriculum Vitae.
%%% Kieran Healy <kjhealy@gmail.com>
%%% Most recent version is at http://kjhealy.github.com/kjh-vita
%%%
%%% ------------------------------------------------------------------------
%%% Requirements (should be included in a modern tex distribution):
%%% ------------------------------------------------------------------------
%%% xelatex
%%% fontspec.sty
%%% hyperrref.sty
%%% xunicode.sty
%%% color.sty
%%% url.sty
%%% fancyhdr.sty
%%%
%%% ------------------------------------------------------------------------
%%% Optional
%%% ------------------------------------------------------------------------
%%% git
%%% vc.sty
%%% revnum.sty
%%% Fonts
%%%
%%% ------------------------------------------------------------------------
%%% Note
%%%------------------------------------------------------------------------
%%% Because this is a hand-tweaked file, be on the look out for \medksip, 
%%% \bigskip and \newpage commands here and there, which are used to balance
%%% the layout or avoid widows & orphans, etc. You should of course add or 
%%% remove these as needed.
%%%------------------------------------------------------------------------

\documentclass[11pt]{article}

%%%------------------------------------------------------------------------
%%% Metadata
%%%------------------------------------------------------------------------

%% Change as needed. Or just add me as a coauthor. Only some of these are 
%% used below in the hyperref declaration and address banner section.
\def\myauthor{Maarten Steenhagen}
\def\mytitle{Vita}
\def\mycopyright{\myauthor}
\def\mykeywords{}
\def\mybibliostyle{plain}
\def\mybibliocommand{}
\def\mysubtitle{}
\def\myaffiliation{University College London}
\def\myaddress{Department of Philosophy}
\def\myemail{m.steenhagen.09@ucl.ac.uk}
\def\myweb{http://ucl.ac.uk/\string~uctymst}
\def\myblog{http://maarten.steenhagen.nl}
\def\myphone{+44 (0)777 1193717}
\def\myfax{~}
\def\myversion{}
\def\myrevision{}

\def\myaffiliation{University College London}
\def\myauthor{Maarten Steenhagen}
\date{} % not used (revision control instead)
\def\mykeywords{Maarten, Steenhagen, Maarten Steenhagen, Vita, CV, Resume, Philosophy}

%%%------------------------------------------------------------------------  
%%% Git version tracking 
%%%------------------------------------------------------------------------

%% If you don't use git or the vc package (from CTAN), comment this out.
%% If you comment it out, be sure to remove the \rfoot comment below, too.
%\input{vc}

%%%------------------------------------------------------------------------
%%% Required style files
%%%------------------------------------------------------------------------
\usepackage{url,fancyhdr}
%%\usepackage{revnum} % for reverse-numbered publications (revnumerate environment) if needed.

%% needed for xelatex to work
\usepackage{fontspec}
\usepackage{xunicode}

%% color for the links 
\usepackage{color}

%% hyperlinks
\usepackage[xetex, 
	colorlinks=false,
	plainpages=false,
  	pdfpagelabels,
  	bookmarksnumbered,
  	pdftitle={\mytitle},
  	pagebackref,
  	pdfauthor={\myauthor},
  	pdfkeywords={\mykeywords}
  	]{hyperref}

%%%------------------------------------------------------------------------
%%% Document
%%%------------------------------------------------------------------------
\begin{document}

%% Choose fonts for use with xelatex
%% Minion and Myriad are widely available, from Adobe. 
%% Pragmata is available to buy at http://www.fsd.it/fonts/pragma.htm
%% and is worth every penny. Any good monospace font will work fine, though.
%% Consolas or inconsolata are good alternatives.
\setromanfont[Mapping={tex-text},Numbers={OldStyle},Ligatures={Common}]{Brill} 
\newfontfamily\margin[Mapping=tex-text,Colour=AA0000, Letters=SmallCaps]{Futura}
\setmonofont[Mapping=tex-text,Scale=0.9]{Helvetica}

% \newcommand{\amps}{\amper{\&}}

%%%------------------------------------------------------------------------
%%% Local commands
%%%------------------------------------------------------------------------

%% Marginal header
%% Note: as the document goes on you may need to introduce a (gradually increasing)
%% \vspace element to keep the marginal header pleasingly aligned with the first 
%% item in the body text. Like this: \marginhead{{\vskip 0.4em}Grants}, or 
%% \marginhead{{\vskip 0.8em}Service}. Experiment as needed.
\newcommand{\marginhead}[1]{\marginpar{\margin{{\footnotesize\vspace{-1em}\flushright #1}}}}

%% custom ampersand (font consistent with the one chosen above)
\newcommand{\amper}{{\fontspec[Scale=.85]{Baskerville Italic}\selectfont\&\,}}

%% No bullets on labels
\renewcommand{\labelitemi}{~}

%% Custom hanging indent for vita items
\def\ind{\hangindent=1 true cm\hangafter=1 \noindent}
%\def\ind{\hangindent=18pt\hangafter=1 \noindent}
\def\labelitemi{~}
\renewcommand{\labelitemii}{~}

%%%------------------------------------------------------------------------
%%% Page layout
%%%------------------------------------------------------------------------
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0pt}
\fancyhead{}
\fancyfoot{}
\rhead{{\scriptsize\thepage}}

%% git revision control footer 
%\rfoot{\texttt{\scriptsize \VCRevision\ on \VCDateTEX}} % git revision info inserted via external script -- see docs for vc package for details. comment out this line if you're not using vc, and also remove the \input{vc} line above.

%%%------------------------------------------------------------------------
%%% Address and contact block
%%%------------------------------------------------------------------------
\begin{minipage}[t]{2.95in}
 \flushright {\footnotesize \href{http://ucl.ac.uk/philosophy}{Department of Philosophy} \\ University College London \\ Gower Street \\ \vspace{-0.05in} London, \textsc{wc1e 6bt}}

\end{minipage}
\hfill     
%\begin{minipage}[t]{0.0in}
% dummy (needed here)
%\end{minipage}
\hfill
\begin{minipage}[t]{1.7in}
  \flushright \footnotesize Phone: \myphone \\  
  {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}}} \\
  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}
	{\scriptsize  \texttt{\href{\myblog}{\myblog}}}
\end{minipage}

\vfil

%% Name 
\noindent{\Large {\textsc{maarten steenhagen}}}
\reversemarginpar

\bigskip

%% Appointments
\medskip

\marginhead{Current Position}

\noindent\emph{University College London \vspace{0.01in}}

\ind Doctoral Candidate (PhD) in Philosophy.

\ind Dissertation research on the nature of human experience of pictorial representations.

\bigskip

\marginhead{AoS}

\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics; Metaethics.

\bigskip
\bigskip

\marginhead{AoC}

\ind Metaphysics; History of Twentieth Century Philosophy; Political Philosophy.

\bigskip
\bigskip
\vfil 
\marginhead{Education \newline (Past)}

\noindent\emph{University College London \vspace{0.01in}}

% \ind 2012--Present. Doctoral Candidate (PhD).

\ind 2012. MPhil Stud. research student. Dissertation: \emph{The Collective Image}. \vspace{-0.1in}

\bigskip

\noindent\emph{University of Utrecht\vspace{0.02in}}

\ind 2009. B.A., Philosophy.

\medskip

\noindent\emph{ARTeZ School of Fine Art\vspace{0.02in}}

\ind 2005. BFA., Fine Art.

\bigskip

\marginhead{Appointments}

\noindent\emph{Heythrop College London \vspace{0.01in}}

\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology.

\ind 2009--Present. Research Assistant in Philosophy.

\medskip

\noindent\emph{University of Kent \vspace{0.01in}}

\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art.

\medskip

\noindent\emph{University College London \vspace{0.01in}}

\ind 2011-2012. Teaching Assistant in Philosophy.

\medskip

\noindent\emph{Utrecht School of Arts \vspace{0.01in}}

\ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.

\medskip

\noindent\emph{University of Utrecht \vspace{0.01in}}

\ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.

\bigskip

\newpage

%% Presentations
\marginhead{{\vskip 0.4em}Talks}
\medskip

\ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)

\ind 2012. ```Non-conceptualised depiction.'' The Queen's College Oxford, Annual conference of the British Society of Aesthetics. September.

\ind 2012. ``Researching the Self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.

\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Philosophical Aesthetics}.

\ind 2011. ``Representing the Trinity.'' University of Ghent, Annual conference of the Dutch Society of Aesthetics.

\ind 2011. ``Truly political? A psychoanalytic understanding of engaged art.'', University of Leeds, \emph{Working Through Psychoanalysis}.

\ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)

\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.

%\end{revnumerate}
\bigskip

\marginhead{{\vskip 0.4em}Grants and \newline Awards}
\medskip

\ind 2012. British Society of Aesthetics PhD Studentship Award. (£36.000)

\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not used.}

\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not used.}

\ind 2010. Dutch Association for Aesthetics Essay Contest, 2$^{\textrm{\tiny{nd}}}$ Prize.

\ind 2009. Huygens Scholarship Programme, Nuffic, The Hague (€30.000).

\bigskip

\marginhead{{\vskip 0.9em}Service to the \newline Profession}
\medskip

\medskip

\ind 2012--Present. Editor of the \emph{Postgraduate Journal of Aesthetics.}

\ind 2010--Present. Co-Organiser London Aesthetics Forum, Institute of Philosophy, London.

\ind 2012--Present. Website Editor London Philosophy and Psychoanalysis Group.

\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (ESPP) Annual Conference 2012, Institute of Philosophy, London.

\ind 2011. UCL Representative for the British Postgraduate Philosophy Association.

\ind 2007-2009. Editor of \emph{Cimedart}, Philosophy Journal of the University of Amsterdam.

% %% Publications
% \marginhead{{\vskip 0.3em}Publications}
% \medskip
% \noindent\emph{Book \vspace{0.01in}}
% 
% \ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{-0.075in}
%  
% \normalsize
% 
% \bigskip
% \noindent\emph{Journal articles \vspace{0.05in}}
%  
% %% Use revnumerate environment if numbered publications are needed. 
% %% (Include it above in the preamble).
% %% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
% %% \begin{revnumerate}
% 
% \ind Marion Fourcade and Kieran Healy. 2007. ``\href{http://arjournals.annualreviews.org/doi/pdf/10.1146/annurev.soc.33.040406.131642}{Moral Views of Market Society}.'' \emph{Annual Review of Sociology} 33:~285--311. 
% 
% \ind Kieran Healy. 2006. ``\href{http://www.kieranhealy.org/files/papers/presumed-consent.pdf}{Do Presumed Consent Laws Raise Organ Procurement Rates?}'' \emph{DePaul Law Review} 55:~1017--1043. 
% 
% \ind Kieran Healy. 2004. ``\href{http://www.kieranhealy.org/files/papers/asr2004.pdf}{Altruism as an Organizational Problem: The Case of Organ Procurement}.''
%  \emph{American Sociological Review} 69:~387--404.
% 
% \ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/jpp.pdf}{Digital Technology and Cultural Goods}.'' \emph{Journal of
%   Political Philosophy} 10:~478--500. 
% 
% \ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/culture-newecon.pdf}{What's New for Culture in the New Economy?}'' \emph{Journal
%   of Arts Management, Law and Society} 32:~86--103. 
% 
% 
% \ind Kieran Healy. 2000. ``\href{http://www.kieranhealy.org/files/papers/embed-alt.pdf}{Embedded Altruism: Blood Collection Regimes and the European
%   Union's Donor Population}.'' \emph{American Journal of Sociology} 105:~1633--\,1657.
% 
% 
% \ind Kieran Healy. 1999.  ``\href{http://www.kieranhealy.org/files/papers/ts.pdf}{The Emergence of \textsc{hiv} in the U.S. Blood Supply: Organizations,
%   Obligations and the Management of Uncertainty}.'' \emph{Theory and Society} 28:~529--558.
% 
% 
% \ind Bruce Western and Kieran Healy. 1999. ``\href{http://www.kieranhealy.org/files/papers/western-healy99.pdf}{Explaining the OECD Wage Slowdown:
% Recession or Labor Decline?}''  \emph{European Sociological Review}
% 15:~233--249.
% 
% 
% \ind  Kieran Healy. 1998.  ``\href{http://www.kieranhealy.org/files/papers/constraint98.pdf}{Conceptualising Constraint: Mouzelis, Archer and the concept of
%   social structure}.'' \emph{Sociology} 32:~509--522. 
% 
% %\end{revnumerate}
% %\newpage
% \bigskip
% 
% \noindent\emph{Book chapters \vspace{0.05in}}
% % \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
% % \begin{revnumerate}
% 
% \ind Kieran Healy. Forthcoming. ``Social Structure, Gifts and Norms in \emph{The Story of Qiu Ju},'' in \emph{Norms and Values: The Role of Social Norms as Instruments of Value Realisation}, edited by Michael Baurmann, Geoffrey Brennan, Robert E. Goodin and Nicholas Southwood. Baden Baden: Nomos Verlag.
% 
% \ind Kieran Healy. 2008. ``Lo Scambio di Doni,'' in \emph{L'Altro in Me: Dono del Sangue fra Culture, Pratiche e Identità}, edited by Annamaria Fantauzzi. Milano: \textsc{avis} Nazionale, 36--42. 
% 
% \ind Kieran Healy. 2007. ``Sociology,'' in \emph{A Companion to Contemporary Political Philosophy} (Second Edition), edited by Robert E. Goodin, Philip Pettit and Thomas Pogge. New York: Blackwell, 90--122. 
% 
% \ind  Kieran Healy. 2004. ``Sacred Markets and Secular Ritual in the Organ Transplant
% Industry,'' in \emph{The Sociology of the Economy}, edited by Frank Dobbin. New
% York: Russell Sage, 336--359.
% 
% \ind Bruce Western and Kieran Healy.  2001.  ``Wage Growth and Labor Decline in the
% Industrialized Democracies, 1965--1993,'' in \emph{Unemployment in the New
%   Europe}, edited by Nancy Bermeo. New York: Cambridge University Press,
% 121--144.
% 
%  \ind  Kieran Healy. 1998. ``The New Institutionalism and Irish Social Policy,'' in
% \emph{Social Policy in Ireland: Principles, Practice and Problems}, edited by
% Se\'{a}n Healy and Brigid Reynolds. Dublin: Oak Tree Press, 59--83.
% 
% %\end{revnumerate}
% 
% \bigskip 
%  
% %\newpage
% \noindent\emph{Reviews and other occasional writing \vspace{0.05in}}
% 
% %\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
% %\begin{revnumerate}
% \ind Kieran Healy. 2009. \href{http://www.journals.uchicago.edu/doi/pdf/10.1086/605757}{Review} of \emph{Pop Finance} by Brooke Harrington. \emph{American Journal of Sociology} 115:~309--12.
% 
% \ind Kieran Healy. 2007. ``\href{http://www.kieranhealy.org/files/reviews/socforum-article.pdf}{A Wealth of Notions}.'' Review
% Essay on \emph{Freakonomics} by Steven Levitt and Stephen Dubner. \emph{Sociological Forum} 22:~119--125. 
% 
% \ind  Kieran Healy. 2006. ``Sacred.'' In \emph{International Encyclopedia of Economic Sociology}, edited by Jens Beckert and Milan Zafirovski. London: Routledge, 588--589. 
% 
% \ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/klinenberg.pdf}{Review} of \emph{Heat Wave} by Eric Klinenberg. \emph{Imprints} 8:~283--289.
% 
% \ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/fox.pdf}{Review} of \emph{An R and S-PLUS Companion to Applied Regression}, by John Fox. \emph{Sociological Methods and Research} 34:~137--140.
% 
% \ind  Kieran Healy. 2005. ``\href{http://www.kieranhealy.org/files/reviews/henwood.pdf}{After the Ball was Over}.'' Review of \emph{After the New
%   Economy} by Doug Henwood. \emph{European Economic Sociology Newsletter} 6 (3):~37--38.
% 
% \ind  Kieran Healy. 2004. ``The Abundance of the Heart.'' Review of \emph{A Man After His Own Heart} by Charles
% Siebert. \emph{Australian Review of Public Affairs}, October. Reprinted in the
% \emph{Australian Financial Review}, October 22nd.
% 
% \ind  Kieran Healy. 2003. \href{http://links.jstor.org/sici?sici=0094-3061%28200303%2932%3A2%3C252%3AAEATOC%3E2.0.CO%3B2-F}{Review} of \emph{Against Essentialism} by Stephan Fuchs.
% \emph{Contemporary Sociology} 32:~252--254.
% 
% \ind  Kieran Healy. 2001. Review of \emph{Market Society} by Don Slater and Fran Tonkiss. \emph{European
%       Economic Sociology Newsletter} 3 (1):~31--32.
% 
% 
% \ind  Kieran Healy. 1999. \href{http://links.jstor.org/sici?sici=0094-3061%28199903%2928%3A2%3C210%3ACPRCAS%3E2.0.CO%3B2-C}{Review} of \emph{Comparative Politics} by Mark Irving Lichbach and Alan S.
% Zuckerman. \emph{Contemporary Sociology} 28:~210--211.
% 
% 
% \ind  Kieran Healy. 1998. \href{http://www.kieranhealy.org/files/reviews/rule.pdf}{Review} of \emph{Theory and Progress in Social Science} by James Rule.  \emph{Theory
%   and Society}, 27:~435--441.
% 
% % %\end{revnumerate}
%  \bigskip

\end{document}

### 2012-10-02 MSteenhagen-CV.tex
Updated information.

@@
 \usepackage[xetex, 
-	colorlinks=false,
+	colorlinks=true,
 	plainpages=false,
@@
 
-\ind Dissertation research on the nature of human experience of pictorial representations.
+\ind Dissertation research on the nature of human experience of pictorial representations. Supervisor: Prof. Mark Eli Kalderon.
 
@@
 
-\bigskip
 \bigskip
@@
 
-\ind 2012. MPhil Stud. research student. Dissertation: \emph{The Collective Image}. \vspace{-0.1in}
+\ind 2012.
+MPhil Stud.
+research student.
+Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.
+Supervisors: Prof.
+Mark Eli Kalderon; Prof.
+Christopher Peacocke.
+\vspace{-0.1in}
 
@@
 
-\newpage
+% \newpage
 
@@
 
+\marginhead{{\vskip 0.3em}Publications}
+\medskip
+
+\ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
+
+\ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
+
+\ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
+
+\bigskip
+
 \marginhead{{\vskip 0.4em}Grants and \newline Awards}
@@
 
-\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not used.}
+\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}
 
-\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not used.}
+\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}
 
@@
 \marginhead{{\vskip 0.9em}Service to the \newline Profession}
-\medskip
-
 \medskip
@@
 
+\ind 2008. Chair of the organisation for \emph{The Philosopher's Rally,} an international graduate conference in Philosophy, Utrecht.
+
+\bigskip
+
+\marginhead{{\vskip 0.9em}IT-Skills}
+\medskip
+
+\ind Microsoft Office Suite; Adobe Acrobat Professional; Adobe Photoshop and Indesign; BibDesk/Endnote and TeX-based typesetting; HTML/PHP; Open Journal Systems.
+
+\bigskip
+
+\marginhead{{\vskip 0.9em}Languages}
+\medskip
+
+\ind Dutch (native); English (fluent); German (good).
+
 % %% Publications
-% \marginhead{{\vskip 0.3em}Publications}
-% \medskip
-% \noindent\emph{Book \vspace{0.01in}}
-% 
-% \ind  Kieran Healy. 2006. \emph{\href{http://www.lastbestgifts.com}{Last Best Gifts: Altruism and the Market for Human Blood and Organs}}. Chicago:~University of Chicago Press. \vspace{-0.075in}
+
 %  

### 2012-10-02 MSteenhagen-CV.tex
Added links. Some revision. Added date-stamp.

@@
 \usepackage{color}
-
+\definecolor{grey}{cmyk}{0,1,0,0.8}
 %% hyperlinks
@@
 	colorlinks=true,
+	urlcolor=grey,
 	plainpages=false,
@@
 
-\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics; Metaethics.
+\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics.
 
@@
 
-\ind Metaphysics; History of Twentieth Century Philosophy; Political Philosophy.
+\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ Century Philosophy; Political Philosophy.
 
@@
 
-\noindent\emph{University College London \vspace{0.01in}}
+\noindent\emph{University College London, Dept. Philosophy \vspace{0.01in}}
 
@@
 
-\noindent\emph{University of Utrecht\vspace{0.02in}}
+\noindent\emph{University of Utrecht, Dept. Philosophy\vspace{0.02in}}
 
@@
 
-\noindent\emph{ARTeZ School of Fine Art\vspace{0.02in}}
+\noindent\emph{ARTeZ School of Fine Art, Dept. Monumental Art\vspace{0.02in}}
 
@@
 
-\noindent\emph{Heythrop College London \vspace{0.01in}}
+\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Dept. Philosophy} \vspace{0.01in}}
 
@@
 
-\noindent\emph{University of Kent \vspace{0.01in}}
+\noindent\href{http://www.kent.ac.uk/arts/hpa/index.html}{\emph{University of Kent, History \amper Philosophy of Art} \vspace{0.01in}}
 
@@
 
-\noindent\emph{University College London \vspace{0.01in}}
+\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Dept. Philosophy}} \vspace{0.01in}
 
@@
 
-\noindent\emph{Utrecht School of Arts \vspace{0.01in}}
+\noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}
 
@@
 
-\noindent\emph{University of Utrecht \vspace{0.01in}}
+\noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}
 
@@
 
-\ind 2012. British Society of Aesthetics PhD Studentship Award. (£36.000)
+\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. (£36.000)
 
@@
 
-\ind 2012--Present. Editor of the \emph{Postgraduate Journal of Aesthetics.}
+\ind 2012--Present. Editor of the \href{http:\\www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics.}}
 
-\ind 2010--Present. Co-Organiser London Aesthetics Forum, Institute of Philosophy, London.
+\ind 2010--Present. Co-Organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.
 
-\ind 2012--Present. Website Editor London Philosophy and Psychoanalysis Group.
+\ind 2012--Present. Website Editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.
 
-\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (ESPP) Annual Conference 2012, Institute of Philosophy, London.
+\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (\href{http://www.eurospp.org}{ESPP}) Annual Conference 2012, Institute of Philosophy, London.
 
-\ind 2011. UCL Representative for the British Postgraduate Philosophy Association.
+\ind 2011. UCL Representative for the \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association}.
 
-\ind 2007-2009. Editor of \emph{Cimedart}, Philosophy Journal of the University of Amsterdam.
+\ind 2007-2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.
 
@@
 
+\rfoot{\footnotesize{\today}}
 % %% Publications

### 2012-12-05 MSteenhagen-CV.tex
Modified AoC.
Blocked out some info.
Added some info to .tex head
Removed foreign entries.
Added Warwick talk
Added Mindgrad

@@
 %%% A template to produce a nice-looking Curriculum Vitae.
-%%% Kieran Healy <kjhealy@gmail.com>
-%%% Most recent version is at http://kjhealy.github.com/kjh-vita
+%%% Orginally produced by Kieran Healy <kjhealy@gmail.com>
+%%% This version is adapted (only minimally) by Maarten Steenhagen.
 %%% 
@@
 
-\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ Century Philosophy; Political Philosophy.
+\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. Philosophy; Political Philosophy.
 
@@
 
-% \newpage
-
+\newpage
 %% Presentations
@@
 \medskip
+
+\ind 2012.
+``Two problems of co-consciousness.'' Department of Philosophy, University of Warwick, \href{http://www2.warwick.ac.uk/fac/soc/philosophy/news/conferences/mindgrad-2012/}{MindGrad 2012}.
+Respondent: Dr.
+Christoph Hoerl (Warwick).
+
+\ind 2012. ``Imaginary Experience.'' University of Warwick, London-Warwick Graduate Mind Forum.
 
@@
 
-\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. (£36.000)
+\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)
 
@@
 \rfoot{\footnotesize{\today}}
-% %% Publications
-
-%  
-% \normalsize
-% 
-% \bigskip
-% \noindent\emph{Journal articles \vspace{0.05in}}
-%  
-% %% Use revnumerate environment if numbered publications are needed. 
-% %% (Include it above in the preamble).
-% %% \renewcommand{\labelenumi}{\textsc{a}\theenumi.}
-% %% \begin{revnumerate}
-% 
-% \ind Marion Fourcade and Kieran Healy.
-2007.
-``\href{http://arjournals.annualreviews.org/doi/pdf/10.1146/annurev.soc.33.040406.131642}{Moral Views of Market Society}.'' \emph{Annual Review of Sociology} 33:~285--311.
-% 
-% \ind Kieran Healy. 2006. ``\href{http://www.kieranhealy.org/files/papers/presumed-consent.pdf}{Do Presumed Consent Laws Raise Organ Procurement Rates?}'' \emph{DePaul Law Review} 55:~1017--1043. 
-% 
-% \ind Kieran Healy. 2004. ``\href{http://www.kieranhealy.org/files/papers/asr2004.pdf}{Altruism as an Organizational Problem: The Case of Organ Procurement}.''
-%  \emph{American Sociological Review} 69:~387--404.
-% 
-% \ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/jpp.pdf}{Digital Technology and Cultural Goods}.'' \emph{Journal of
-%   Political Philosophy} 10:~478--500. 
-% 
-% \ind Kieran Healy. 2002. ``\href{http://www.kieranhealy.org/files/papers/culture-newecon.pdf}{What's New for Culture in the New Economy?}'' \emph{Journal
-%   of Arts Management, Law and Society} 32:~86--103. 
-% 
-% 
-% \ind Kieran Healy. 2000. ``\href{http://www.kieranhealy.org/files/papers/embed-alt.pdf}{Embedded Altruism: Blood Collection Regimes and the European
-%   Union's Donor Population}.'' \emph{American Journal of Sociology} 105:~1633--\,1657.
-% 
-% 
-% \ind Kieran Healy. 1999.  ``\href{http://www.kieranhealy.org/files/papers/ts.pdf}{The Emergence of \textsc{hiv} in the U.S. Blood Supply: Organizations,
-%   Obligations and the Management of Uncertainty}.'' \emph{Theory and Society} 28:~529--558.
-% 
-% 
-% \ind Bruce Western and Kieran Healy. 1999. ``\href{http://www.kieranhealy.org/files/papers/western-healy99.pdf}{Explaining the OECD Wage Slowdown:
-% Recession or Labor Decline?}''  \emph{European Sociological Review}
-% 15:~233--249.
-% 
-% 
-% \ind  Kieran Healy. 1998.  ``\href{http://www.kieranhealy.org/files/papers/constraint98.pdf}{Conceptualising Constraint: Mouzelis, Archer and the concept of
-%   social structure}.'' \emph{Sociology} 32:~509--522. 
-% 
-% %\end{revnumerate}
-% %\newpage
-% \bigskip
-% 
-% \noindent\emph{Book chapters \vspace{0.05in}}
-% % \renewcommand{\labelenumi}{\textsc{c}\theenumi.}
-% % \begin{revnumerate}
-% 
-% \ind Kieran Healy.
-Forthcoming.
-``Social Structure, Gifts and Norms in \emph{The Story of Qiu Ju},'' in \emph{Norms and Values: The Role of Social Norms as Instruments of Value Realisation}, edited by Michael Baurmann, Geoffrey Brennan, Robert E.
-Goodin and Nicholas Southwood.
-Baden Baden: Nomos Verlag.
-% 
-% \ind Kieran Healy. 2008. ``Lo Scambio di Doni,'' in \emph{L'Altro in Me: Dono del Sangue fra Culture, Pratiche e Identità}, edited by Annamaria Fantauzzi. Milano: \textsc{avis} Nazionale, 36--42. 
-% 
-% \ind Kieran Healy.
-2007.
-``Sociology,'' in \emph{A Companion to Contemporary Political Philosophy} (Second Edition), edited by Robert E.
-Goodin, Philip Pettit and Thomas Pogge.
-New York: Blackwell, 90--122.
-% 
-% \ind  Kieran Healy. 2004. ``Sacred Markets and Secular Ritual in the Organ Transplant
-% Industry,'' in \emph{The Sociology of the Economy}, edited by Frank Dobbin. New
-% York: Russell Sage, 336--359.
-% 
-% \ind Bruce Western and Kieran Healy.  2001.  ``Wage Growth and Labor Decline in the
-% Industrialized Democracies, 1965--1993,'' in \emph{Unemployment in the New
-%   Europe}, edited by Nancy Bermeo. New York: Cambridge University Press,
-% 121--144.
-% 
-%  \ind  Kieran Healy. 1998. ``The New Institutionalism and Irish Social Policy,'' in
-% \emph{Social Policy in Ireland: Principles, Practice and Problems}, edited by
-% Se\'{a}n Healy and Brigid Reynolds. Dublin: Oak Tree Press, 59--83.
-% 
-% %\end{revnumerate}
-% 
-% \bigskip 
-%  
-% %\newpage
-% \noindent\emph{Reviews and other occasional writing \vspace{0.05in}}
-% 
-% %\renewcommand{\labelenumi}{\textsc{r}\theenumi.}
-% %\begin{revnumerate}
-% \ind Kieran Healy. 2009. \href{http://www.journals.uchicago.edu/doi/pdf/10.1086/605757}{Review} of \emph{Pop Finance} by Brooke Harrington. \emph{American Journal of Sociology} 115:~309--12.
-% 
-% \ind Kieran Healy. 2007. ``\href{http://www.kieranhealy.org/files/reviews/socforum-article.pdf}{A Wealth of Notions}.'' Review
-% Essay on \emph{Freakonomics} by Steven Levitt and Stephen Dubner. \emph{Sociological Forum} 22:~119--125. 
-% 
-% \ind  Kieran Healy. 2006. ``Sacred.'' In \emph{International Encyclopedia of Economic Sociology}, edited by Jens Beckert and Milan Zafirovski. London: Routledge, 588--589. 
-% 
-% \ind  Kieran Healy. 2005. \href{http://www.kieranhealy.org/files/reviews/klinenberg.pdf}{Review} of \emph{Heat Wave} by Eric Klinenberg. \emph{Imprints} 8:~283--289.
-% 
-% \ind  Kieran Healy.
-2005.
-\href{http://www.kieranhealy.org/files/reviews/fox.pdf}{Review} of \emph{An R and S-PLUS Companion to Applied Regression}, by John Fox.
-\emph{Sociological Methods and Research} 34:~137--140.
-% 
-% \ind  Kieran Healy. 2005. ``\href{http://www.kieranhealy.org/files/reviews/henwood.pdf}{After the Ball was Over}.'' Review of \emph{After the New
-%   Economy} by Doug Henwood. \emph{European Economic Sociology Newsletter} 6 (3):~37--38.
-% 
-% \ind  Kieran Healy. 2004. ``The Abundance of the Heart.'' Review of \emph{A Man After His Own Heart} by Charles
-% Siebert. \emph{Australian Review of Public Affairs}, October. Reprinted in the
-% \emph{Australian Financial Review}, October 22nd.
-% 
-% \ind  Kieran Healy. 2003. \href{http://links.jstor.org/sici?sici=0094-3061%28200303%2932%3A2%3C252%3AAEATOC%3E2.0.CO%3B2-F}{Review} of \emph{Against Essentialism} by Stephan Fuchs.
-% \emph{Contemporary Sociology} 32:~252--254.
-% 
-% \ind  Kieran Healy. 2001. Review of \emph{Market Society} by Don Slater and Fran Tonkiss. \emph{European
-%       Economic Sociology Newsletter} 3 (1):~31--32.
-% 
-% 
-% \ind  Kieran Healy. 1999. \href{http://links.jstor.org/sici?sici=0094-3061%28199903%2928%3A2%3C210%3ACPRCAS%3E2.0.CO%3B2-C}{Review} of \emph{Comparative Politics} by Mark Irving Lichbach and Alan S.
-% Zuckerman. \emph{Contemporary Sociology} 28:~210--211.
-% 
-% 
-% \ind  Kieran Healy. 1998. \href{http://www.kieranhealy.org/files/reviews/rule.pdf}{Review} of \emph{Theory and Progress in Social Science} by James Rule.  \emph{Theory
-%   and Society}, 27:~435--441.
-% 
-% % %\end{revnumerate}
-%  \bigskip
 

### 2013-02-14 MSteenhagen-CV.tex
Added Ockham Society talk
Added editorship PJA and membership P&PGroup

@@
 
-\ind Dissertation research on the nature of human experience of pictorial representations. Supervisor: Prof. Mark Eli Kalderon.
+\ind Dissertation research on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.
 
+\bigskip
+
+\ind Editor, \href{http://www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics}}
+
+\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
+
+\bigskip
 \bigskip
@@
 
+\bigskip
 \bigskip
@@
 \medskip
+\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.
 

### 2013-02-15 MSteenhagen-CV.tex
Blocked out 'publications'
Added teaching fields, blocked out some talks (now fits on 2 pages again)

@@
 
-\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology.
+\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).
 
-\ind 2009--Present. Research Assistant in Philosophy.
+\ind 2009--Present. Research Assistant in Philosophy\\ (Philosophy of psychology, Clinical methodology, Psychoanalysis)
 
@@
 
-\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art.
+\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art (Aesthetics)
 
@@
 
-\ind 2011-2012. Teaching Assistant in Philosophy.
+\ind 2011-2012. Teaching Assistant in Philosophy (Applied Ethics)
 
-\medskip
-
-\noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}
-
-\ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.
-
-\medskip
-
-\noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}
-
-\ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.
+% \medskip
+% 
+% \noindent\href{http://www.hku.nl/web/English.htm}{\emph{Utrecht School of Arts} \vspace{0.01in}}
+% 
+% \ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.
+% 
+% \medskip
+% 
+% \noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}
+% 
+% \ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.
 
@@
 %% Presentations
-\marginhead{{\vskip 0.4em}Talks}
+\marginhead{{\vskip 0.4em}Talks (recent)}
 \medskip
@@
 
-\ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
-
-\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
+% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
+% 
+% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
 
@@
 
-\marginhead{{\vskip 0.3em}Publications}
-\medskip
-
-\ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
-
-\ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
-
-\ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
-
-\bigskip
+% \marginhead{{\vskip 0.3em}Publications}
+% \medskip
+% 
+% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
+% 
+% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
+% 
+% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
+% 
+% \bigskip
 

### 2013-02-15 MSteenhagen-CV.tex
Created (and moved) professional organitions section

@@
 \bigskip
-
-\ind Editor, \href{http://www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics}}
-
-\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
-
-\bigskip
 \bigskip
@@
 \ind 2005. BFA., Fine Art.
+
+\bigskip
 
@@
 
-\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Philosophical Aesthetics}.
+\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Aesthetics}.
 
-\ind 2011. ``Representing the Trinity.'' University of Ghent, Annual conference of the Dutch Society of Aesthetics.
+\ind 2011. ``Representing the Trinity.'' University of Ghent, NGE Annual conference .
 
@@
 % \bigskip
+\marginhead{Professional organisations}
+\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
+
+\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}
+
+\bigskip
 

### 2013-04-05 MSteenhagen-CV.tex
Fixed hyphen
Swapped memberships around
Added Birkbeck worskhop presentation
Slight modification of dissertation description
Minor change in appointment description

@@
 
-\ind Dissertation research on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.
+\ind Dissertation on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.
 
@@
 
-\ind 2009--Present. Tutorial Assistant in Philosophy and Psychology\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).
+\ind 2009--Present. Tutorial Assistant in Philosophy\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).
 
@@
 \medskip
+\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)
+
 \ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.
@@
 \marginhead{Professional organisations}
-\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
 
 \ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}
+
+\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
 
@@
 
-\ind 2007-2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.
+\ind 2007--2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.
 

### 2013-04-10 MSteenhagen-CV.tex
AOS/AOC adjustment
Blocked out 2012 response to Lamb (to keep it two pages)
Fixed typo in CV (MPhil Stud completion year)
Reformulated dissertation focus

@@
 
-\ind Dissertation on the nature of human experience of pictorial representation. Supervisor: Prof. Mark Eli Kalderon.
+\ind Dissertation on the perceptual nature of pictorial representation.\\ Supervisor: Prof. Mark Eli Kalderon.
 
@@
 
-\ind Philosophy of Psychology; Philosophy of Mind \amper Language; Aesthetics.
+\ind Philosophy of psychology; Philosophy of perception; Aesthetics.
 
@@
 
-\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. Philosophy; Political Philosophy.
+\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language.
 
@@
 
-\ind 2012.
+\ind 2011.
 MPhil Stud.
@@
 
-\ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)
+% \ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)
 

### 2013-04-10 MSteenhagen-CV.tex
Education label change
Fixed 'department of's

@@
 \vfil 
-\marginhead{Education \newline (Past)}
+\marginhead{Education}
 
-\noindent\emph{University College London, Dept. Philosophy \vspace{0.01in}}
+\noindent\emph{University College London, Department of  Philosophy \vspace{0.01in}}
 
@@
 
-\noindent\emph{University of Utrecht, Dept. Philosophy\vspace{0.02in}}
+\noindent\emph{University of Utrecht, Department of  Philosophy\vspace{0.02in}}
 
@@
 
-\noindent\emph{ARTeZ School of Fine Art, Dept. Monumental Art\vspace{0.02in}}
+\noindent\emph{ARTeZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}
 
@@
 
-\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Dept. Philosophy} \vspace{0.01in}}
+\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}
 
@@
 
-\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Dept. Philosophy}} \vspace{0.01in}
+\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Department of  Philosophy}} \vspace{0.01in}
 

### 2013-04-10 MSteenhagen-CV.tex
Fixed MPhil Stud qualification
Fixed ArtEZ typo
Reformulated TA Heythr description

@@
 \ind 2011.
-MPhil Stud.
-research student.
+MPhil Stud., Philosophy.
 Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.
@@
 
-\noindent\emph{ARTeZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}
+\noindent\emph{ArtEZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}
 
@@
 
-\ind 2009--Present. Tutorial Assistant in Philosophy\\ (Psychoanalysis, Metaethics, Perception \& epistemology, Descartes).
+\ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.
 

### 2013-04-10 MSteenhagen-CV.tex
Reform. Heyth. RA description
Further refomulations of teaching experience

@@
 
-\ind 2009--Present. Research Assistant in Philosophy\\ (Philosophy of psychology, Clinical methodology, Psychoanalysis)
+\ind 2009--Present. Research Assistant in Philosophy, working on philosophy of psychology, clinical methodology and psychoanalysis.
 
@@
 
-\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art (Aesthetics)
+\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art, seminar leader and lecturer in aesthetics)
 
@@
 
-\ind 2011-2012. Teaching Assistant in Philosophy (Applied Ethics)
+\ind 2011-2012. Teaching Assistant in Philosophy, seminar leader applied ethics
 

### 2013-04-10 MSteenhagen-CV.tex
Teaching experience; moved RA to back
Moved professional organisations to back

@@
 
-\marginhead{Appointments}
+\marginhead{Teaching experience}
 
@@
 \ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.
-
-\ind 2009--Present. Research Assistant in Philosophy, working on philosophy of psychology, clinical methodology and psychoanalysis.
 
@@
 
-\ind 2012. ``Imaginary Experience.'' University of Warwick, London-Warwick Graduate Mind Forum.
+\ind 2012. ``Imaginary experience.'' University of Warwick, London-Warwick Graduate Mind Forum.
 
@@
 
-\ind 2012. ``Researching the Self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.
+\ind 2012. ``Researching the self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.
 
@@
 
-\ind 2011. ``Representing the Trinity.'' University of Ghent, NGE Annual conference .
+\ind 2011. ``Representing the trinity.'' University of Ghent, NGE Annual conference .
 
@@
 % \bigskip
-\marginhead{Professional organisations}
-
-\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}
-
-\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
-
-\bigskip
 
@@
 
+\ind 2012--Present. Website Editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.
+
 \ind 2010--Present. Co-Organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.
 
-\ind 2012--Present. Website Editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.
+\ind 2009--Present. Research Assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.
 
@@
 \ind 2008. Chair of the organisation for \emph{The Philosopher's Rally,} an international graduate conference in Philosophy, Utrecht.
+
+\bigskip
+
+\marginhead{Professional organisations}
+
+\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}
+
+\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
 

### 2013-04-10 MSteenhagen-CV.tex
Fixed wishful thinking about start date PhD
Work exp
Fixed caps and typo in Work experience

@@
 
-\ind 2012. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)
+\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)
 
-\ind 2012. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}
+\ind 2011. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}
 
-\ind 2012. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}
+\ind 2011. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}
 
@@
 
-\marginhead{{\vskip 0.9em}Service to the \newline Profession}
+\marginhead{{\vskip 0.9em}Work experience}
 \medskip
@@
 
-\ind 2012--Present. Website Editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.
+\ind 2012--Present. Website editor \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy and Psychoanalysis Group}.
 
-\ind 2010--Present. Co-Organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.
+\ind 2010--Present. Co-organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.
 
-\ind 2009--Present. Research Assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.
+\ind 2009--Present. Research assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.
 
-\ind 2012. Assistant Organiser European Society for Philosophy and Psychology (\href{http://www.eurospp.org}{ESPP}) Annual Conference 2012, Institute of Philosophy, London.
+\ind 2012. Assistant organiser European Society for Philosophy and Psychology (\href{http://www.eurospp.org}{ESPP}) Annual Conference 2012, Institute of Philosophy, London.
 
@@
 
-\ind 2008. Chair of the organisation for \emph{The Philosopher's Rally,} an international graduate conference in Philosophy, Utrecht.
+\ind 2008. Chair of the organisation for \emph{The Philosophers' Rally,} an international graduate conference in Philosophy, Utrecht.
 

### 2013-04-10 MSteenhagen-CV.tex
Blocked out ESPP and BPPA stuff
Unblocked ESPP
BPPA stuff now in prof. org.
Several changes

@@
 MPhil Stud., Philosophy.
-Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.
-Supervisors: Prof.
+Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.\\ Supervisors: Prof.
 Mark Eli Kalderon; Prof.
@@
 
-\noindent\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}
-
-\ind 2009--Present. Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.
+\ind 2009--Present.
+Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.
+\href{http://www.heythrop.ac.uk/departments/academic-departments/philosophy/}{\emph{Heythrop College London, Department of  Philosophy} \vspace{0.01in}}
 
@@
 
-\noindent\href{http://www.kent.ac.uk/arts/hpa/index.html}{\emph{University of Kent, History \amper Philosophy of Art} \vspace{0.01in}}
-
-\ind 2011--2012. Assistant Lecturer, History and Philosophy of Art, seminar leader and lecturer in aesthetics)
+\ind 2011--2012.
+Assistant Lecturer, History and Philosophy of Art, seminar leader and lecturer in Aesthetics.
+\href{http://www.kent.ac.uk/arts/hpa/index.html}{\emph{University of Kent, History \amper Philosophy of Art} \vspace{0.01in}}
 
@@
 
-\noindent\href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Department of  Philosophy}} \vspace{0.01in}
-
-\ind 2011-2012. Teaching Assistant in Philosophy, seminar leader applied ethics
+\ind 2011-2012. Teaching Assistant in Philosophy, seminar leader Applied Ethics. \href{http://www.ucl.ac.uk/philosophy/}{\emph{University College London, Department of  Philosophy}} \vspace{0.01in}
 
@@
 
-\newpage
+%\newpage
 %% Presentations
@@
 
-\ind 2011. UCL Representative for the \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association}.
-
 \ind 2007--2009. Editor of \href{http://www.cimedart.nl}{\emph{Cimedart}}, Philosophy Journal of the University of Amsterdam.
@@
 \ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{London Philosophy \& Psychoanalysis Group}
+
+\ind Representative, \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association} (UCL, 2011).
 

### 2013-04-11 MSteenhagen-CV.tex
Some punctuation

@@
 
-\noindent\emph{University College London \vspace{0.01in}}
+\ind Doctoral Candidate (PhD) in Philosophy, \emph{University College London \vspace{0.01in}}
 
-\ind Doctoral Candidate (PhD) in Philosophy.
-
-\ind Dissertation on the perceptual nature of pictorial representation.\\ Supervisor: Prof. Mark Eli Kalderon.
+\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon
 
@@
 
-\ind Philosophy of psychology; Philosophy of perception; Aesthetics.
+\ind Philosophy of psychology; Philosophy of perception; Aesthetics
 
@@
 
-\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language.
+\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language
 
@@
 
-\noindent\emph{University College London, Department of  Philosophy \vspace{0.01in}}
-
 % \ind 2012--Present. Doctoral Candidate (PhD).
@@
 MPhil Stud., Philosophy.
-Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.\\ Supervisors: Prof.
+Dissertation: \href{http://discovery.ucl.ac.uk/1348204/}{\emph{The Collective Image}}.
+\emph{University College London, Department of  Philosophy \vspace{0.01in}}\\ Supervisors: Prof.
 Mark Eli Kalderon; Prof.
@@
 
-\noindent\emph{University of Utrecht, Department of  Philosophy\vspace{0.02in}}
-
-\ind 2009. B.A., Philosophy.
+\ind 2009. B.A., Philosophy. \emph{University of Utrecht, Department of  Philosophy\vspace{0.02in}}
 
@@
 
-\noindent\emph{ArtEZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}
-
-\ind 2005. BFA., Fine Art.
+\ind 2005. BFA., Fine Art. \emph{ArtEZ School of Fine Art, Department of Monumental Art\vspace{0.02in}}
 
@@
 
+\marginhead{{\vskip 0.4em}Scholarships \newline and awards}
+\medskip
+
+\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award. %(£36.000)
+
+\ind 2011. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}
+
+\ind 2011. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}
+
+\ind 2010. Dutch Association for Aesthetics Essay Contest, 2$^{\textrm{\tiny{nd}}}$ Prize.
+
+\ind 2009. Huygens Scholarship Programme, Nuffic, The Hague (€30.000).
+
 \bigskip
 
+%\newpage
+%% Presentations
+\marginhead{{\vskip 0.4em}Research \newline presentations}
+\medskip
+\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)
+
+\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.
+
+\ind 2012.
+``Two problems of co-consciousness.'' Department of Philosophy, University of Warwick, \href{http://www2.warwick.ac.uk/fac/soc/philosophy/news/conferences/mindgrad-2012/}{MindGrad 2012}.
+Respondent: Dr Christoph Hoerl (Warwick).
+
+\ind 2012. ``Imaginary experience.'' University of Warwick, London-Warwick Graduate Mind Forum.
+
+% \ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)
+
+\ind 2012. ```Non-conceptualised depiction.'' The Queen's College Oxford, Annual conference of the British Society of Aesthetics. September.
+
+\ind 2012. ``Researching the self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.
+
+\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Aesthetics}.
+
+\ind 2011. ``Representing the trinity.'' University of Ghent, NGE Annual conference .
+
+\ind 2011. ``Truly political? A psychoanalytic understanding of engaged art.'', University of Leeds, \emph{Working Through Psychoanalysis}.
+
+% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
+% 
+% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
+
+%\end{revnumerate}
+\bigskip
 \marginhead{Teaching experience}
@@
 
-%\newpage
-%% Presentations
-\marginhead{{\vskip 0.4em}Talks (recent)}
-\medskip
-\ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)
-
-\ind 2013. ``Pictures \& perceptual knowledge'' The Ockham Society, Department of Philosophy, University of Oxford.
-
-\ind 2012.
-``Two problems of co-consciousness.'' Department of Philosophy, University of Warwick, \href{http://www2.warwick.ac.uk/fac/soc/philosophy/news/conferences/mindgrad-2012/}{MindGrad 2012}.
-Respondent: Dr.
-Christoph Hoerl (Warwick).
-
-\ind 2012. ``Imaginary experience.'' University of Warwick, London-Warwick Graduate Mind Forum.
-
-% \ind 2012. ``How the five die: Response to Lamb.'' University College London, 2012 Graduate Conference in Philosophy. (Response paper.)
-
-\ind 2012. ```Non-conceptualised depiction.'' The Queen's College Oxford, Annual conference of the British Society of Aesthetics. September.
-
-\ind 2012. ``Researching the self.'' St. John's College Oxford, \emph{Art as a Mode of Enquiry}.
-
-\ind 2011. ``Seeing what another would.'' Utrecht University, \emph{Expert Meeting on Aesthetics}.
-
-\ind 2011. ``Representing the trinity.'' University of Ghent, NGE Annual conference .
-
-\ind 2011. ``Truly political? A psychoanalytic understanding of engaged art.'', University of Leeds, \emph{Working Through Psychoanalysis}.
-
-% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
-% 
-% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
-
-%\end{revnumerate}
-\bigskip
-
 % \marginhead{{\vskip 0.3em}Publications}
@@
 
-\marginhead{{\vskip 0.4em}Grants and \newline Awards}
-\medskip
-
-\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} PhD Studentship Award. %(£36.000)
-
-\ind 2011. Prins Bernhard Cultuurfonds (€10.000). \emph{Not taken up.}
-
-\ind 2011. Hendrik Müller Vaderlandsch Fonds (€5.000). \emph{Not taken up.}
-
-\ind 2010. Dutch Association for Aesthetics Essay Contest, 2$^{\textrm{\tiny{nd}}}$ Prize.
-
-\ind 2009. Huygens Scholarship Programme, Nuffic, The Hague (€30.000).
-
-\bigskip
-
-\marginhead{{\vskip 0.9em}Work experience}
+\marginhead{{\vskip 0.9em}Work \newline experience}
 \medskip

### 2013-04-28 MSteenhagen-CV.tex
Some more minor changes and punctuation fixes
Made planned submission date more explicit
Added Utrecht teaching experience to CV

@@
 
-\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon
+\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2014
 
@@
 
-\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ C. philosophy; Philosophy of language
+\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ c. philosophy; Philosophy of language
 
@@
 %% Presentations
-\marginhead{{\vskip 0.4em}Research \newline presentations}
+\marginhead{{\vskip 0.4em}Research \newline presentations \newline(recent)}
 \medskip
@@
 % \ind 2008-2009. Assistant Lecturer in Art Theory and Cultural History.
-% 
 % \medskip
 % 
-% \noindent\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Dept. Philosophy} \vspace{0.01in}}
-% 
-% \ind 2007-2008. Teaching Assistant in Aesthetics and Moral Psychology.
+\ind 2007-2008.
+Teaching Assistant in Aesthetics.
+\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}
+
+\ind 2008.
+Teaching Assistant in Moral Psychology.
+\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}
+
+\ind 2007.
+Teaching Assistant in Philosophy of Science.
+\href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}
 
@@
 
-\ind Representative, \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association} (UCL, 2011).
+\ind Representative, \href{http://www.bppa-online.org}{British Postgraduate Philosophy Association} (UCL, 2011)
 

### 2013-09-25 MSteenhagen-CV.tex
Changed Utrecht teaching experience on CV
Updated CV September 2013 (For refs appls)

@@
 
+\ind 2013. \href{http://www.ucl.ac.uk/ah/figs/homepage}{UCL Faculty of Arts and Humanities} Postgraduate Research Studentship. %(£36.000)
+
 \ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award. %(£36.000)
@@
 \medskip
+
+\ind 2013. ``Response to Renault--Steele'' American Society of Aesthetics annual conference, Department of Philosophy, University of California at San Diego. (Invited response.)
+
+\ind 2013. ``Unthought thoughts'' Annual conference of the European Society for Philosophy and Psychology, University of Granada, Spain.
+
+\ind 2013. ``Looking like: response to Sethi'' Berkeley-London Graduate Conference in Philosophy, Department of Philosophy, University of California at Berkeley. (Invited response.)
+
 \ind 2013. ``Changing one's ways'' Workshop \emph{Skills, Habits, and Action Explanation}, Department of Philosophy, Birkbeck College London. (Response paper.)
@@
 \ind 2007.
-Teaching Assistant in Philosophy of Science.
+Teaching Assistant and seminar leader in Philosophy of Science.
 \href{http://www.uu.nl/faculty/humanities/EN/organisation/departments/departmentofphilosophy/Pages/default.aspx}{\emph{University of Utrecht, Department of  Philosophy}} \vspace{0.01in}
@@
 \medskip
+
+\ind 2013--Present. Member of the Advisory Counsil, Institute of Philosophy, London.
+
+\ind 2013--Present. Website Manager for the \href{http://www.british-aesthetics.org.uk}{British Society of Aesthetics.}
 
@@
 
-\ind Member, \href{http://www.philosophy-psychoanalysis.org.uk}{British Society of Aesthetics}
+\ind Non-voting member of the board of Trustees, \href{http://www.british-aesthetics.org.uk}{British Society of Aesthetics}
 

### 2013-12-23 MSteenhagen-CV.tex
Updated CV

@@
 
-\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2014
+\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2015
 
@@
 
-% \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
-% 
-% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
+\ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
+
+\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
 
@@
 
-\ind 2009--Present.
+\ind 2009--2013.
 Tutorial Assistant, teaching Metaethics, Epistemology of Perception, Descartes and Psychoanalysis.
@@
 
+\ind Member of the Oxford-Sydney Research Group on Empathy and Sympathy.
+
 \ind Non-voting member of the board of Trustees, \href{http://www.british-aesthetics.org.uk}{British Society of Aesthetics}

### 2015-10-03 MSteenhagen-CV.tex
Updated date
New CV added

--- 2013-09-25 MSteenhagen-CV.tex
@@
 
-\documentclass[11pt]{article}
+\documentclass[12pt]{article}
 
@@
 \def\mysubtitle{}
-\def\myaffiliation{University College London}
-\def\myaddress{Department of Philosophy}
-\def\myemail{m.steenhagen.09@ucl.ac.uk}
-\def\myweb{http://ucl.ac.uk/\string~uctymst}
+\def\myaffiliation{University of Antwerp}
+\def\myaddress{Centre for Philosophical Psychology}
+\def\myemail{maartensteenhagen@gmail.com}
+\def\myweb{http://msteenhagen.github.io}
 \def\myblog{http://maarten.steenhagen.nl}
-\def\myphone{+44 (0)777 1193717}
+\def\myphone{+44 (0)78 66 425161}
 \def\myfax{~}
@@
 
-\def\myaffiliation{University College London}
+% \def\myaffiliation{University of Antwerp}
 \def\myauthor{Maarten Steenhagen}
@@
 \usepackage{xunicode}
-
+\usepackage{multicol}
 %% color for the links 
@@
 \begin{minipage}[t]{2.95in}
- \flushright {\footnotesize \href{http://ucl.ac.uk/philosophy}{Department of Philosophy} \\ University College London \\ Gower Street \\ \vspace{-0.05in} London, \textsc{wc1e 6bt}}
+ \flushright {\footnotesize {Centre for Philosophical Psychology} \\ University of  Antwerp \\ Stadscampus \\ Lange Sint-Annastraat 7, S.S.208 \\ \vspace{-0.05in} 2000 Antwerp, Belgium}
 
@@
   {\scriptsize  \texttt{\href{mailto:\myemail}{\myemail}}} \\
-  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}
-	{\scriptsize  \texttt{\href{\myblog}{\myblog}}}
+  {\scriptsize  \texttt{\href{\myweb}{\myweb}}}\\
+	{\scriptsize  skype: \texttt{maartensteenhagen}}
 \end{minipage}
 
-\vfil
-
+\bigskip  
 %% Name 
@@
 
-\ind Doctoral Candidate (PhD) in Philosophy, \emph{University College London \vspace{0.01in}}
+\ind Research Fellow\\
+Centre for Philosophical Psychology\\
+University of Antwerp
 
-\ind Dissertation on the perceptual nature of pictorial representation\\ Supervisor: Prof. Mark Eli Kalderon\\Projected submission: Autumn 2014
+\vspace{0.01in}
 
-\bigskip
-\bigskip
+\medskip
 
@@
 
-\ind Philosophy of psychology; Philosophy of perception; Aesthetics
+\ind Philosophy of perception; Philosophy of psychology; Aesthetics
 
@@
 
-\ind Metaphysics; Metaethics; History of 20$^{\textrm{\tiny{th}}}$ c. philosophy; Philosophy of language
+\ind Metaphysics; History of analytic philosophy; Philosophy of language
+
+% \ind Supervisor: Prof. Mark Eli Kalderon
+% 
+% \ind Expected: Spring 2015
+% 
+% \bigskip
+\bigskip
+\bigskip
+
+\marginhead{{\vskip 0.3em}Publications}
+\medskip
+% 
+\ind (forthcoming) `Psycho-analysis, philosophy, and the pictorial arts' in: Lacewing, Gibbs, Steenhagen (eds.) \emph{The Oxford Handbook of Philosophy and Psychoanalysis}. Oxford University Press.
+
+\ind (forthcoming) \emph{The Oxford Handbook of Philosophy and Psychoanalysis}. Oxford University Press. (Associate editor)
+
+\ind  (forthcoming). `Review of Lambert Wiesing's \emph{Sehen Lassen},' in: \emph{British Journal of Aesthetics}. DOI: 10.1093/aesthj/ayu016
+
+\ind  (2010). `Explaining the ugly: disharmony and unrestrained cognition in Kant' in: \emph{Esthetica} (November).
 
 \bigskip
-\bigskip
-\vfil 
 \marginhead{Education}
@@
 % \ind 2012--Present. Doctoral Candidate (PhD).
+
+\ind 2014-2015. Visiting Research Student in the Department of Philosophy at the University of Toronto. Advisor: Mohan Matthen.
+
+\ind 2011-2015. Ph.D., Philosophy. Dissertation:
+\emph{Appearance and Representation}. 
+\emph{University College London, Department of  Philosophy \vspace{0.01in}}\\ Advisors: Prof. Mark Eli Kalderon; Prof. Mohan Matthen (Toronto)\\
+Examiners: Prof. John Hyman (Oxford); Prof. David Papineau (KCL) 
+\vspace{-0.1in}
+
+\begin{quote}
+	\textsc{abstract:} In this dissertation I examine the relation between two concepts that are indispensable both to the philosophy of perception and to philosophical aesthetics: appearance and representation.
+Either implicitly or explicitly, philosophers have disagreed over whether representations play any significant role in our perception of objects, events or properties.
+In this work I show that imagistic representations, such as photographs, paintings, and drawings, indeed play a significant part in our perception of the items we encounter in the world.
+My main claim is that such images fulfil a mediating function in vision, allowing us to perceive the scenes they represent by means of them.
+Images enable us visually to perceive scenes not present to the sense of sight, and in this way introduce into the world the possibility for a distinctive kind of visual appearance.
+\end{quote}
 
@@
 Mark Eli Kalderon; Prof.
-Christopher Peacocke.
-\vspace{-0.1in}
+Christopher Peacocke \vspace{-0.1in}
 
@@
 
+% \marginhead{{\vskip 0.3em}Publications}
+% \medskip
+% %
+% \ind (forthcoming) \emph{The Oxford Handbook of Philosophy and Psychoanalysis}. Oxford University Press. (Associate editor)
+%
+% \ind  (forthcoming). `Review of Lambert Wiesing's \emph{Sehen Lassen},' in: \emph{British Journal of Aesthetics}. DOI: 10.1093/aesthj/ayu016
+%
+% \ind  (2010). `Explaining the ugly: disharmony and unrestrained cognition in Kant' in: \emph{Esthetica} (November).
+% 
+% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
+% 
+% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
+% 
+% \bigskip
+
 \marginhead{{\vskip 0.4em}Scholarships \newline and awards}
@@
 
-\ind 2013. \href{http://www.ucl.ac.uk/ah/figs/homepage}{UCL Faculty of Arts and Humanities} Postgraduate Research Studentship. %(£36.000)
+\ind 2015. Jacobsen Studentship, Royal Institute of Philosophy, London (£9000).
 
-\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award. %(£36.000)
+\ind 2014. American Philosophical Association, Postgraduate bursary (\$400).
+
+\ind 2013. \href{http://www.ucl.ac.uk/ah/figs/homepage}{UCL Faculty of Arts and Humanities} Postgraduate Research Studentship (£5000) %(£36.000)
+
+\ind 2011. \href{http://www.british-aesthetics.org}{British Society of Aesthetics} Two-year PhD Studentship Award (£36.000).
 
@@
 %% Presentations
-\marginhead{{\vskip 0.4em}Research \newline presentations \newline(recent)}
+\marginhead{{\vskip 0.4em}Talks \newline(recent)}
 \medskip
 
-\ind 2013. ``Response to Renault--Steele'' American Society of Aesthetics annual conference, Department of Philosophy, University of California at San Diego. (Invited response.)
+\ind 2016. ``False reflections'' American Philosophical Association, Eastern Division Meeting, San Diego. (Upcoming)
+
+\ind 2015. ``Collingwood, sympathy, and the work of art'' INSEI workshop on empathy and interpretation. Cambridge, UK
+
+\ind 2014. ``Source representationalism'' Postgraduate Sessions of the Joint Session of the Aristotelian Society and Mind Association, University of Cambridge.
+
+\ind 2014. ``Thoughts you don't think'' American Philosophical Association, Pacific Division Meeting, San Diego. Respondent: Dr. Katherine Rickus (Marquette)
+
+% \ind 2013. ``Response to Renault--Steele'' American Society of Aesthetics annual conference, Department of Philosophy, University of California at San Diego. (Invited response.)
 
@@
 % \ind 2010. ``Photography and dull causation: Response to Atencia-Linares.'' University College London, 2010 Graduate Conference in Philosophy. (Response paper.)
-% 
-% \ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
+
+\ind 2010. ``Explaining the Ugly: Disharmony and Unrestrained Cognition in Kant.'' Institute of Philosophy, London-Berkeley Graduate Conference in Philosophy.
 
@@
 
-% \marginhead{{\vskip 0.3em}Publications}
-% \medskip
-% 
-% \ind  Steenhagen, M. 2010. `Explaining the Ugly,' \emph{Esthetica,} November.
-% 
-% \ind  Steenhagen, M. 2009. `Verwarring over lelijkheid,' \emph{Cimedart,} 39:2.
-% 
-% \ind  Steenhagen, M. 2008. `De keerzijde van liefde,' \emph{Cimedart,} 38:3.
-% 
-% \bigskip
+\marginhead{{\vskip 0.9em}Professional \newline experience}
+\medskip
 
-\marginhead{{\vskip 0.9em}Work \newline experience}
-\medskip
+\ind 2014--Present. Referee for \emph{British Journal of Aesthetics} and \emph{Topoi}.
 
@@
 
-\ind 2012--Present. Editor of the \href{http:\\www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics.}}
+\ind 2012--2015. Editor of the \href{http:\\www.pjaesthetics.org}{\emph{Postgraduate Journal of Aesthetics.}}
 
@@
 
-\ind 2010--Present. Co-organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.
+\ind 2010--2015. Co-organiser \href{http:\\www.londonaestheticsforum.org}{London Aesthetics Forum}, Institute of Philosophy, London.
 
-\ind 2009--Present. Research assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.
+\ind 2009--2015. Research assistant in Philosophy at Heythrop College London. Working on philosophy of psychology, clinical methodology and psychoanalysis.
 
@@
 \marginhead{Professional organisations}
+
+\ind Interdisciplinary Network on Sympathy, Empathy and Imagination (INSEI).
 
